E exp 3

### 2018-08-31 experiments/A_pilot_1/writeup/A_pilot_1.Rmd
consistent YAML

```{r load libraries, message=FALSE, warning=FALSE}
library(knitr)
library(tidyverse)
library(broom)
library(broom.mixed)
library(lme4)
library(lmerTest)
library(dotwhisker)
library(kableExtra)
library(LMERConvenienceFunctions)
library(data.table)
library(gridExtra)
source('summarySEwithin2.R')
source("A_pilot_1_functions/pretty_coef_table.R")
```

>>>>

```{r load libraries, message=FALSE, warning=FALSE}
library(knitr)
library(tidyverse)
library(broom)
library(broom.mixed)
library(lme4)
library(lmerTest)
library(dotwhisker)
library(kableExtra)
library(LMERConvenienceFunctions)
library(data.table)
library(grid)
library(gridExtra)
source('summarySEwithin2.R')
source("A_pilot_1_functions/pretty_coef_table.R")
```

### 2018-08-31 experiments/B_pilot_2/writeup/B_pilot_2.Rmd
consistent YAML

```{r pander, echo=FALSE, cache=FALSE, message=FALSE}
library(knitr)
library(tidyverse)
library(broom)
library(broom.mixed)
library(lme4)
library(lmerTest)
library(dotwhisker)
library(kableExtra)
library(LMERConvenienceFunctions)
library(data.table)
library(gridExtra)
source('summarySEwithin2.R')
source("B_pilot_2_functions/pretty_coef_table.R")
```

>>>>

```{r pander, echo=FALSE, cache=FALSE, message=FALSE}
library(knitr)
library(tidyverse)
library(broom)
library(broom.mixed)
library(lme4)
library(lmerTest)
library(dotwhisker)
library(kableExtra)
library(LMERConvenienceFunctions)
library(data.table)
library(grid)
library(gridExtra)
source('summarySEwithin2.R')
source("B_pilot_2_functions/pretty_coef_table.R")
```

### 2018-08-31 experiments/C_exp_1/writeup/C_exp_1.Rmd
consistent YAML

```{r 'load Libraries and source my functions', message=FALSE, echo=FALSE}
library(knitr)
library(tidyverse)
library(broom)
library(broom.mixed)
library(lme4)
library(lmerTest)
library(dotwhisker)
library(kableExtra)
library(LMERConvenienceFunctions)
library(data.table)
library(gridExtra)
source("C_exp_1_functions/concatenate_raw_data.R")
source("C_exp_1_functions/annotate_the_raw_data.R")
source("C_exp_1_functions/add_borderline_vars.R")
source("C_exp_1_functions/pretty_coef_table.R")
source("C_exp_1_functions/summarySEwithin2.R")
root_dir <- getwd()
data_dir <- "C_exp_1_data"
```

>>>>

```{r 'load Libraries and source my functions', message=FALSE, echo=FALSE}
library(knitr)
library(tidyverse)
library(broom)
library(broom.mixed)
library(lme4)
library(lmerTest)
library(dotwhisker)
library(kableExtra)
library(LMERConvenienceFunctions)
library(data.table)
library(grid)
library(gridExtra)
source("C_exp_1_functions/concatenate_raw_data.R")
source("C_exp_1_functions/annotate_the_raw_data.R")
source("C_exp_1_functions/add_borderline_vars.R")
source("C_exp_1_functions/pretty_coef_table.R")
source("C_exp_1_functions/summarySEwithin2.R")
root_dir <- getwd()
data_dir <- "C_exp_1_data"
```

### 2018-08-31 experiments/E_exp_3/writeup/E_exp_3.Rmd
consistent YAML

---
title: "E exp 3"
author: "Matt Green"
output:
  html_document:
    toc: true
    toc_float: false
---

```{r, "libs and functions", echo=FALSE, message=FALSE}
library(knitr)
library(tidyverse)
library(broom)
library(broom.mixed)
library(lme4)
library(lmerTest)
library(dotwhisker)
library(kableExtra)
library(LMERConvenienceFunctions)
library(data.table)
library(gridExtra)
source("E_exp_3_functions/preprocessing.R")
source("E_exp_3_functions/pretty_coef_table.R")
source("E_exp_3_functions/summarySEwithin2.R")
root_dir <- getwd()
data_dir <- "E_exp_3_data"
```

>>>>

---
title: "E exp 3"
author: "Matt Green"
output:
  html_document:
    toc: true
    theme: default
    css: styles.css
---

```{r, "libs and functions", echo=FALSE, message=FALSE}
library(knitr)
library(tidyverse)
library(broom)
library(broom.mixed)
library(lme4)
library(lmerTest)
library(dotwhisker)
library(kableExtra)
library(LMERConvenienceFunctions)
library(data.table)
library(grid)
library(gridExtra)
source("E_exp_3_functions/preprocessing.R")
source("E_exp_3_functions/pretty_coef_table.R")
source("E_exp_3_functions/summarySEwithin2.R")
root_dir <- getwd()
data_dir <- "E_exp_3_data"
```
